---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MpoxModelPack

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/vanessaxiu/mpox-model-package.svg?branch=main)](https://travis-ci.com/vanessaxiu/mpox-model-package)
[![Codecov test coverage](https://codecov.io/gh/vanessaxiu/mpox-model-package/branch/main/graph/badge.svg)](https://app.codecov.io/gh/vanessaxiu/mpox-model-package?branch=main)
<!-- badges: end -->

The goal of MpoxModelPack is to build a deterministic compartmental model that retrospectively assesses the impact of behavourial changes and non-pharmaceutical interventions, e.g. contact tracing, vaccinations.

## Installation

You can install the development version of MpoxModelPack from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("vanessaxiu/MpoxModelPack")
```

## Example

This is a basic example which loads contact rates and proportion in all three cities:

```{r}
library(MpoxModelPack)
init.pop.fn()
```

